Early Observations of \abc:\\ \textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-10-26 doc/ms.tex
Update text regarding power-law fit to observations

The time of first light, interpreted in this study as the moment when appreciable heating from $^{56}$Ni decay has first diffused to the photosphere, for SNe is usually estimated by 
extrapolating early-phase light curves to determine when the 
SN flux is equal to 0. Assuming an ideal, expanding fireball with 
constant temperature, \citet{1982ApJ...253..785A} derives that $f 
\propto t^2$, where $f$ is the SN flux and $t$ is the time since 
explosion. Despite the basic assumption of a constant temperature at 
early times, multiple studies have found that the early emission 
from Type Ia SNe can be described as a power law in time, with 
power-law index consistent with 2, i.e. $f \propto t^2$ (e.g., \citealt{2006AJ....132.1707C, 2010ApJ...712..350H, 2011MNRAS.416.2607G}).\footnote{Many of the studies that find $f \propto t^2$ sample SNe Ia light curves at a phase that is closer to $T_{B,\mathrm{max}}$ than the initial observations of \abc\ discussed here.}

As our observations include especially early observations of \abc, there are upper limits $\sim$1 d prior to the discovery epoch, we model the early flux from \abc\ as a power law, but allow the power-law index to vary, as opposed to fixing it at 2, to account for potential variations in the photospheric temperature during expansion:
\begin{equation}
  \label{eq:broken_power_law}
  f(t) \left\{
    \begin{array}{ll}
      = 0,\ \textrm{when}\ t \le t_0 \\
      \propto (t-t_0)^{\alpha},\ \textrm{when}\ t>t_0
    \end{array}
  \right.\ ,
\end{equation}
where $t_0$ is the time of first light, $\alpha$ is the power-law index, and $t$ is measured in the SN rest-frame. To determine $t_0$ and $\alpha$ we fit the earliest observations of \abc. Due to slight variations in the passbands, we fit the model only to the relative flux measured in the $g_\mathrm{PTF}$-band, which is the only filter with observations prior to first light, a necessity for constraining $t_0$.

To determine the best fit parameters, we search a large grid over $t_0$, $\alpha$,
and the proportionality constant, and minimize $\chi^2$. 
The modeling results show that the SN flux rises approximately
linearly between
$t=-18\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit} shows the best-fit result and
the joint marginal distribution of $t_0$ and $\alpha$. From the
best-fit model we obtain $\alpha=0.98 \pm ^{0.16}_{0.14}$ and $t_0=-17.91 \pm ^{0.07}_{0.15}$ d, where the uncertainties represent the marginalized 95\% confidence intervals. Our first
detection of \abc\ occurred $\sim$${0.15}\,\textrm{d}$ after 
the SN first light. 
% Figure~\ref{fig:early_lc_fit} additionally shows $g'$-bands observations from P60 and LCO, where we have normalized the flux assuming that the $g$ magnitudes from each instrument have the same zero-point. This assumption is incorrect (see \S\ref{sec:obs}), and, as expected, the residuals show a systematic offset between the $g_\mathrm{PTF}$-band and the $g'$-band. Nevertheless, if we ignore this systematic and fit all of the $g$-band observations simultaneously we obtain marginalized best-fit parameters that are consistent within the uncertainties with the $g_\mathrm{PTF}$-only values above.
In the analysis that follows, the precise values of the best-fit parameters are not important. The critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \, \mathrm{d}$.

@@

Simulations presented in \citet{2017arXiv170603613N} show that the flux from SNe Ia explosion models does not evolve as a power law in time. Despite this non-power-law evolution, \citet{2017arXiv170603613N} show that $f \propto t^\alpha$ models produce good formal fits to simulated observations. The $f \propto t^\alpha$ fits to the \citeauthor{2017arXiv170603613N} models result in glaring errors to the estimated explosion times. Despite the caution advised in \citet{2017arXiv170603613N}, we proceed with the power-law fits from above for several reasons. (1) Our primary aim with the fit is to characterize $\alpha$ for \abc\ compared to SN\,2011fe (see below). (2) The errors in the estimated explosion times from \citeauthor{2017arXiv170603613N} increase the later the first observation of the SN is obtained. \citeauthor{2017arXiv170603613N} only present fits to observations that start $>$2~d after explosion, whereas the discovery epoch for \abc\ is likely much earlier than that (see \S\ref{sec:early_vel}). (3) We do not use the fits to estimate the time of explosion, $t_0$ instead is an estimate of the time of first light. (4) Pre-discovery upper limits, which are not included in \citeauthor{2017arXiv170603613N}, provide additional strong constraints on the time of first light. Finally, (5) \citet{2017arXiv170603613N} find that models with strong $^{56}$Ni mixing do follow a power-law evolution, and we explore, and argue in favor of, this possibility for \abc\ (see \S\ref{sec:Ni_mixing}).

>>>>

The time of first light for SNe is usually estimated by extrapolating
early-phase light curves to determine when the SN flux is equal to 0.
Assuming an ideal, expanding fireball with constant temperature,
\citet{1982ApJ...253..785A} derives that $f \propto t^2$, where $f$ is the SN
flux and $t$ is the time since explosion. Despite the basic assumption of a
constant temperature at early times, multiple studies have found that the
early emission from Type Ia SNe can be described as a power law in time, with
power-law index consistent with 2, i.e. $f \propto t^2$ (e.g.,
\citealt{2006AJ....132.1707C, 2010ApJ...712..350H,
2011MNRAS.416.2607G}).\footnote{Many of the studies that find $f \propto t^2$
sample SNe Ia light curves at a phase that is closer to $T_{B,\mathrm{max}}$
than the initial observations of \abc\ discussed here.}

As our observations include especially early observations of \abc, there are
upper limits $\sim$1 d prior to the discovery epoch, we model the early flux
from \abc\ as a power law, but allow the power-law index to vary:
\begin{equation}
  \label{eq:broken_power_law}
  f(t) \left\{
    \begin{array}{ll}
      = 0,\ \textrm{when}\ t \le t_0 \\
      \propto (t-t_0)^{\alpha},\ \textrm{when}\ t>t_0
    \end{array}
  \right.\ ,
\end{equation}
where $t_0$ is the time of first light, $\alpha$ is the power-law index, and
$t$ is measured in the SN rest-frame. \textbf{We allow $\alpha$ to vary to
find the best match to the data, and later show that models with $\alpha = 2$
do not explain the data.} To determine $t_0$ and $\alpha$ we fit the earliest
observations of \abc. Due to slight variations in the passbands, we fit the
model only to the relative flux measured in the $g_\mathrm{PTF}$-band, which
is the only filter with observations prior to first light, a necessity for
constraining $t_0$.

To determine the best fit parameters, we search a large grid over $t_0$,
$\alpha$, and the proportionality constant, and minimize $\chi^2$. The
modeling results show that the SN flux rises approximately linearly between
$t=-18\,\textrm{d}$ and $t=-15\,\textrm{d}$. Figure \ref{fig:early_lc_fit}
shows the best-fit result and the joint marginal distribution of $t_0$ and
$\alpha$. From the best-fit model we obtain $\alpha=0.98 \pm ^{0.16}_{0.14}$
and $t_0=-17.91 \pm ^{0.07}_{0.15}$ d, where the uncertainties represent the
marginalized 95\% confidence intervals. Our first detection of \abc\ occurred
$\sim$${0.15}\,\textrm{d}$ after the SN first light. In the analysis that
follows, the precise values of the best-fit parameters are not important. The
critical finding here is that $\alpha \approx 1$ and $t_0 \approx -18 \,
\mathrm{d}$.

@@

Simulations presented in \citet{2017arXiv170603613N} show that the flux from
SNe Ia explosion models does not evolve as a power law in time. Despite this
non-power-law evolution, \citet{2017arXiv170603613N} show that $f \propto
t^\alpha$ models produce good formal fits to simulated observations. The $f
\propto t^\alpha$ fits to the \citeauthor{2017arXiv170603613N}\ models result
in glaring errors to the estimated explosion times. Despite the caution
advised in \citet{2017arXiv170603613N}, we proceed with the power-law fits
from above for several reasons. (1) Our primary aim with the fit is to
characterize $\alpha$ for \abc\ compared to SN\,2011fe (see below). (2) The
errors in the estimated explosion times from \citeauthor{2017arXiv170603613N}
increase the later the first observation of the SN is obtained.
\citeauthor{2017arXiv170603613N} only present fits to observations that start
$>$2\,d after explosion, whereas the discovery epoch for \abc\ is likely much
earlier than that (see \S\ref{sec:early_vel}). (3) We do not use the fits to
estimate the time of explosion, $t_0$ instead is an estimate of the time of
first light. \textbf{Finally,} (4) Pre-discovery upper limits, which are not
included in \citeauthor{2017arXiv170603613N}, provide additional strong
constraints on the time of first light.
